Hidden Talents Multiverse Analysis

### 2021-07-13 manuscript/manuscript.Rmd
add a statement about two-sided p-values

To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)). Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions. For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall *p*-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see [Statistical Inferences](#inference)).

>>>>

To facilitate interpretation of multiverse results, we report median standardized $\beta$s, median 95% confidence intervals, and percent significant for each term in our model (see Table \@ref(tab:table2)). Percent significant refers to the number of analyses (out of `r length(multi_data_list)`) that resulted in a significant effect (two-sided *p*-value < .05) for a particular term and reflects the relative sensitivity (or robustness) of an effect to arbitrary data processing decisions. For the main effects of adversity and task version × adversity interactions, we used a bootstrapping technique[@simonsohn2020; @orben2019; @orben2019a] to compute overall *p*-values, which indicate whether a $\beta$ of a term is larger than expected given the null (the median $\beta$ = 0; see [Statistical Inferences](#inference)).
